\documentclass[12pt]{article}

\setlength{\parindent}{0em}
\setlength{\parskip}{.5em}

\usepackage{framed}
\newcounter{problem}
\newcounter{problempart}[problem]
\newcounter{solutionpart}[problem]
\newenvironment{problem}{\stepcounter{problem}\noindent{\bf\arabic{problem}.}}{\setcounter{problempart}{0}\setcounter{solutionpart}{0}}
\newenvironment{solution}{\par\textcolor{green!50!black}\bgroup}{\egroup\par}
\newcommand{\qpart}{\stepcounter{problempart}${}$\\\noindent{(\alph{problempart})} }
\newcommand{\spart}{\stepcounter{solutionpart}${}$\\\noindent{(\alph{solutionpart})} }
\newcommand{\TODO}{\textcolor{red}{$\blacksquare$}}
\newcommand{\SOL}[1]{\textcolor{green!50!black}{#1}}

\usepackage{hyperref}
\usepackage{fullpage}
\usepackage{amsmath,mathabx,MnSymbol}
\usepackage{color,tikz}
\usepackage{pstricks}
\usepackage{pst-plot,pst-node}
\usepackage{footnote,enumitem}
\usepackage{longtable}
\newcommand{\mx}[1]{\begin{pmatrix}#1\end{pmatrix}}
\definecolor{dkgreen}{rgb}{0,.5,0}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}

\newcommand{\uu}{\mathbf{u}}
\newcommand{\vv}{\mathbf{v}}
\newcommand{\cc}{\mathbf{c}}
\newcommand{\ww}{\mathbf{w}}
\newcommand{\xx}{\mathbf{x}}
\newcommand{\zz}{\mathbf{z}}
\newcommand{\ee}{\mathbf{e}}
\newcommand{\pp}{\mathbf{p}}
\newcommand{\qq}{\mathbf{q}}
\renewcommand{\AA}{\mathbf{A}}
\newcommand{\BB}{\mathbf{B}}
\newcommand{\nn}{\mathbf{n}}
\newcommand{\gp}[1]{\left(#1\right)}

\newcommand{\TODOL}[1]{\textcolor{red}{\underline{\hspace{#1 cm}}}}

\usepackage{listings}

\lstset{
  language=C++,
  showstringspaces=false,
  identifierstyle=\color{magenta},
  basicstyle=\color{magenta},
  keywordstyle=\color{blue},
  identifierstyle=\color{black},
  commentstyle=\color{green},
  stringstyle=\color{red}
}

\begin{document}

\title{CS130 - LAB - Programming Prep}
\date{}
\author{Name: \TODOL7\qquad\qquad SID: \TODOL4}
\maketitle
\begin{center}
\end{center}

\newcommand{\CM}[1]{\textcolor{blue}{\texttt{#1}}}

In this course there will be several programming assignments that involve completing the implementation of functions in a larger body of existing code. This assignment will require you to familiarize yourself with the code used in the next assignment.

Before you begin, you will need to decide what environment you will be using for programming and compiling. If you aren't familiar with seting up programming environments, you can use UCR's cs130 server. Please see the document ``Programming Assignments on cs130.cs.ucr.edu''on Canvas for more information. If you choose to use a different environment, you are responsible for setting up the environment and installing the appropriate libraries.

\begin{enumerate}
\item If necessary, download or upload the hw-1 archive from Canvas to the environment you plan to use for programming assignments.
\item Extract the hw-1 archive and navigate to the newly extracted '1' directory.
\item Look through all the code files ('h' and 'cpp' extensions) and find all the locations with ``TODO''. In only those files, add the following header to the top of the file (fill in your information appropriately):
\begin{verbatim}
// Student Name: [Your name]
// Student ID: [Your ID]
\end{verbatim}
\item Which file defines the struct ``Debug\_Scope''?
  \begin{solution}
  \textbf{\textcolor{red}{\TODO}}
  \end{solution}
\item Which file defines the global constant ``small\_t''?
  \begin{solution}
  \textbf{\textcolor{red}{\TODO}}
  \end{solution}
\item How can you use the ray\_tracer program to compare a test file to a solution image?
  \begin{solution}
  \textbf{\textcolor{red}{\TODO}}
  \end{solution}
\item What additional output is generated when you do this?
  \begin{solution}
  \textbf{\textcolor{red}{\TODO}}
  \end{solution}
\item What should the Object member function  ``Intersection'' do if there are no intersections? It is okay if you don't understand why yet.
  \begin{solution}
  \textbf{\textcolor{red}{\TODO}}
  \end{solution}
\item What should the Box member function  ``Union'' do?
  \begin{solution}
  \textbf{\textcolor{red}{\TODO}}
  \end{solution}
\item Where is the variable ``all\_objects'' declared, and what should you use it for?
  \begin{solution}
  \textbf{\textcolor{red}{\TODO}}
  \end{solution}
\item What does the ``componentwise\_min'' function do?
  \begin{solution}
  \textbf{\textcolor{red}{\TODO}}
  \end{solution}

\item Compile the code using the provided ``SConstruct'' file. Include a screenshot of your successful compilation.
\item Run the provided grading-script.py file on the directory included with the assignment that contains test files.
\item Make a sub-directory named ``hw-1''.
\item Copy only the ``h'' and ``cpp'' files from the assignment directory to ``hw-1''.
\item Create a zip or tar archive file containing the ``hw-1'' directory and the answers to the math review questions and the questions in this document. This archive file should be named something like ``[yournetid]-hw-1.zip'' (ex: ``jgoul004-hw-1.zip''). If you were to run the command ``unzip -l [yournetid]-hw-1.zip'' on a properly constructed archive file, the output should look something like this:
\begin{verbatim}
Archive:  jgoul004-hw-1.zip
  Length      Date    Time    Name
---------  ---------- -----   ----
        0  2023-01-08 09:35   hw-1/
     1198  2023-01-08 09:35   hw-1/box.cpp
     1036  2023-01-08 09:35   hw-1/box.h
     1178  2023-01-08 09:35   hw-1/camera.cpp
     1732  2023-01-08 09:35   hw-1/camera.h
      193  2023-01-08 09:35   hw-1/color.h
     3108  2023-01-08 09:35   hw-1/dump_png.cpp
      213  2023-01-08 09:35   hw-1/dump_png.h
      425  2023-01-08 09:35   hw-1/fixed_color.h
      396  2023-01-08 09:35   hw-1/flat_shader.cpp
      550  2023-01-08 09:35   hw-1/flat_shader.h
      737  2023-01-08 09:35   hw-1/hit.h
      379  2023-01-08 09:35   hw-1/light.h
     5974  2023-01-08 09:35   hw-1/main.cpp
     1408  2023-01-08 09:35   hw-1/misc.h
     1340  2023-01-08 09:35   hw-1/object.h
     2988  2023-01-08 09:35   hw-1/parse.cpp
     4021  2023-01-08 09:35   hw-1/parse.h
      545  2023-01-08 09:35   hw-1/plane.cpp
      505  2023-01-08 09:35   hw-1/plane.h
      672  2023-01-08 09:35   hw-1/ray.h
      812  2023-01-08 09:35   hw-1/registration.cpp
     1255  2023-01-08 09:35   hw-1/render_world.cpp
     1428  2023-01-08 09:35   hw-1/render_world.h
      423  2023-01-08 09:35   hw-1/shader.h
      516  2023-01-08 09:35   hw-1/sphere.cpp
      518  2023-01-08 09:35   hw-1/sphere.h
     4514  2023-01-08 09:35   hw-1/vec.h
   108478  2023-01-08 09:38   jgoul004-math-review.pdf
    52091  2023-01-08 09:38   jgoul004-code-intro.pdf
---------                     -------
   198633                     30 files
\end{verbatim}
\item Submit this archive file to Canvas as your homework 1 submission.
\end{enumerate}

\end{document}
